Monitoring and Projecting Global Hunger: Are We On Track?

### 2021-07-16 docs/test/modeling_fies.tex
resubmission

% Use datatool to read in reported values
% csv must have columns `var` and `val`
\usepackage{datatool}
\DTLsetseparator{,}
\DTLloaddb{data}{vars.csv}
\newcommand{\myvar}[1]{\DTLfetch{data}{var}{#1}{val}}

\addbibresource{library.bib}

@@

Food security has traditionally been difficult to measure, and this has arguably led to an incomplete or possibly inaccurate assessment of global hunger. Metrics of macro-health, such as anthropometric measures and mortality rates are correlated broadly with food insecurity and have been used for many years to monitor human well-being \citep{Puffer1973, Habicht1974}.  However, these metrics are affected by other determinants of health such as the occurrence of infectious diseases, and are not meaningful at the scale of individuals or households \citep{Perumal2018}.  Other proxies for food security, such as food availability estimated from crop yields \citep{Maxwell1992}, are also inadequate because they only make rough estimates of how accessible food is to the general population, and can elide populations that are food insecure due to poor access, even when aggregate food availability is high \citep{Sen1983}.  Moreover, these metrics are very sensitive to incorrect estimates of crop yields and food reserves at a national scale.  Thus, global estimates of hunger and food insecurity based on these metrics carry forward similar flaws.

As researchers began to focus on food insecurity at the individual and household level, microdata from household surveys collecting information on household finances and consumption became a basis to compute a common proxy for food security \citep{Haddad1994}.  However, these efforts were criticized for being onerous, insufficiently comparable, as well as for ignoring subjective and experiential aspects of food security \citep{Maxwell1996}.  This led to the emergence of several indicators designed to be rapidly deployable, and based on the lived experience of food security \citep{Jones2013}.  These metrics include the Household Food Security Survey Module (HFSSM) \citep{kennedy2005keynote}, originally developed for use in the US; the Latin American and Caribbean Food Security Scale (ELCSA); and the Household Food Insecurity and Access Scale (HFIAS) \citep{Coates2007}.

Drawing on the insights derived in designing and implementing these novel food security metrics, the FIES was developed by the Food and Agricultural Organization (FAO) of the United Nations (UN) \citep{Ballard2013} and is now recognized as a rapidly deployable and cross-culturally valid tool for understanding individual and household-level food insecurity \citep{wambogo2018validity, smith2017world}.  The FIES is based on a survey of eight behaviors indicative of food insecurity and hunger over the previous year, such as skipping meals or worrying about having enough to eat.  Processing the responses given to the FIES questions through the Rasch model, each individual in the survey is assigned a score that allows them to be ranked on a scale of food insecurity severity. Once the severity measures are calibrated against a common reference (the global FIES reference scale) \citep{Cafiero2018} and individuals are ranked in this fashion, conventional thresholds for ``moderate'' and ``severe'' food insecurity are set and the prevalence of such food insecurity conditions can be computed. Thresholds are set in such a way that a moderately food insecure respondent is one who likely has compromised on food quality and variety as a result of lack of resources, has been unsure about their ability to obtain food and has skipped meals or run out of food occasionally. A severely food insecure one is likely to have run out of food and has gone an entire day without eating at times during the year.  The percentage of people estimated to be over the threshold set for moderate food insecurity includes people that are also over the threshold for severe food insecurity and represents the SDG indicator 2.1.2.

@@

\subsection{Disaggregation}
The data on the FIES collected by Gallup on behalf of FAO also records many individual-level attributes from the respondents, including age, gender, wealth quintile, and whether they live in an urban or rural area.  Using national data on these variables, a standard weighting scheme is created for each individual, based on the ratio of population probabilities to sample probabilities of an individual with those characteristics being selected \citep{bethlehem2009applied}.  This ensures that the results are representative at a national level.  We use a similar methodology, except that we calculate post-stratification weights at a subnational level.  We use year-specific subnational estimates of population shares by gender, age, urbanization, and, where available, wealth, and create a separate set of weights for each subnational area across all individuals.  For age and gender, we used gridded data from WorldPop \citep{Tatem2017}; for urbanization, we used spatially explicit estimates of population in urban and rural pixels published by Jones and O'Neill and deriving from night-time lights and buffered settlement centroids \citep{Jones2016}; and for wealth we used data on household wealth quintiles from Demographic and Health Surveys \citep{dhsall}.  This methodology rests on the mild assumption that, within a given country, two individuals of the same age, gender, urbanization level and wealth quintile will have a similar food security status, an assumption that underlies much of survey weighting methodology \citep{bethlehem2009applied}.

\subsection{Covariates}
We model subnational rates of moderate and severe food insecurity as a function of several covariates related to human development, nutrition, health, infrastructure, income levels and distribution, and the environment (See Table \ref{tab:covars}).  We employ covariates for which projections are available up to year 2030 and, in most cases, also have subnational spatial resolution.  For projections based on the Shared Socioeconomic Pathways (SSP) framework \citep{oneill2014new}, we use the middle-of-the-road pathway, SSP2, and for climatological variables, we use forecasts based on the Representative Concentration Pathway (RCP) 6.0 \citep{van2011representative}.

@@

For the climatic variables, mean annual temperature and total annual precipitation, we combine historical observations with an ensemble of four bias-corrected simulations of the future climate from the Inter-Sectoral Impact Model Intercomparison Project (ISIMIP) \citep{warszawski2014inter}.  These variables cannot speak to sudden shocks but do capture the climatic baselines relevant to agro-ecological conditions that constrain food production.

Finally, we adjust several variables to account for the effects of the COVID-19 pandemic.  These include June 2020 GDP predictions from the World Bank \citep{prospects2020}, August 2020 estimates of impacts on anthropometry from \textit{The Lancet} \citep{headey2020impacts}, as well as the Poverty Headcount Index \citep{Cuaresma2018}.

@@

\subsection{Modeling}
We fit two models for all subnational areas globally from 2010 to 2030: one for the percent of the population over the threshold for moderate food insecurity, and one for the percent of the population over the threshold for severe food insecurity.  We use both random forest regressions and LASSO (Least Absolute Shrinkage and Selection Operator) regressions, with the results of the LASSO regressions presented in the supplement.   A random forest regression involves generating a large number of decision trees, each using different sub-samples of the data, and then aggregating the predictions of the decision trees.  This approach performs well in the presence of non-linearities and interaction effects among predictor variables \citep{hastie2009elements}.  By taking an ensemble of decision tree models, random forests introduce more variance and balance out the bias that is common to methods based on single decision trees \citep{friedman2001elements}. Given the bounded nature of our variables of interest, the random forest regression are applied to the logistically transformed rates.  We create our models using the \texttt{randomForestSRC} package in R \citep{ishwaran2019randomforestsrc}.

@@

When performing cross validation, it is typical to select observations at random.  However, in our training data we have multiple highly similar observations from each country across years and subnational areas, and we extend our model predictions to countries that were not found at all in our training data.  Thus, we perform a type of leave-one-out cross validation, where we leave out all of the data from one country for each iteration.  Thus, the model error after cross validation gives us a sense of how the model is performing in countries where FIES data was not collected.  By this validation metric, we find that our models perform well, with an $R^2$ of \myvar{rf_cv_mod_rsq} and mean average error (MAE) of \myvar{rf_cv_mod_mae} for moderate food insecurity and an $R^2$ of \myvar{rf_cv_sev_rsq} and a MAE of \myvar{rf_cv_sev_mae} for severe food insecurity.  After fitting models on the entire dataset, we observe a within-sample $R^2$ of \myvar{rf_wthn_mod_rsq} and an MAE of \myvar{rf_wthn_mod_mae} for moderate food insecurity and an $R^2$ of \myvar{rf_wthn_sev_rsq} and a MAE of \myvar{rf_wthn_sev_mae} for severe food insecurity.

After fitting the models, we examine the importance of the individual covariates in explaining rates of moderate and severe food insecurity. We use a common method of permutating each individual variable and re-running the regressions, and then determining the difference in MAE between the regression \citep{ishwaran2007variable, breiman2001random}.  This metric can provide some interpretability to model predictions.

@@

\section{Results}
\subsection{Food Insecurity over Time}
Globally, in the year 2020, we estimate that \myvar{glob_2020_sev} million people are above the threshold for severe food insecurity, and \myvar{glob_2020_mod} billion people are above the threshold for moderate food insecurity (See Fig. \ref{fig:timeseries}). These numbers are higher than the estimates in the 2020 FAO State of Food Insecurity (SOFI) report, which reports about 746 million severely food insecure people and 2 billion people experiencing at least moderate food insecurity in 2019 \citep{sofi2020}.

Under realistic scenario assumptions, we find recent increases in the number of moderate and severely food insecure people around the world, yet expect overall decreases from 2010 to 2030.  These changes are more slight for people who are at least moderately food insecure: in 2030, the number of moderately food insecure people will have decreased by \myvar{decprc_2010_2030_mod}\% since 2010, and the number of severely food insecure people will have decreased by \myvar{decprc_2010_2030_sev}\%.  While the number of moderately and severely food insecure people are modeled to decrease overall, they are projected to increase in lower income countries through 2030.

\begin{figure}[H]
  \centering
  \includegraphics[width=\linewidth]{TimeSeries.pdf}
  \caption{Number of people over the thresholds for moderate and severe food insecurity, by World Bank income groups as of 2020.  Panel (A) shows the number of food insecure people with region totals stacked, to show global trends and totals over time.  Panel (B) shows regional totals compared against each other over time.}
  \label{fig:timeseries}
\end{figure}

@@

\begin{figure}[H]
  \centering
  \includegraphics[width=\linewidth]{Rates.pdf}
  \caption{Percentage of the population over the threshold for moderate and severe food insecurity, by World Bank income groups as of 2020.}
  \label{fig:rates}
\end{figure}

@@

\begin{landscape}
\begin{figure}[h]
  \centering
  \includegraphics[width=\linewidth]{FullMap.pdf}
  \caption{Spatial distribution of moderate and severe food insecurity for the years 2010, 2020, and 2030.}
  \label{fig:map}
\end{figure}
\end{landscape}

\subsection{Important Predictors of Food Insecurity}
Overall, our model was able to predict food insecurity with high accuracy in the countries for which training data was available ($R^2 = \myvar{rf_wthn_mod_rsq}$ and $R^2 = \myvar{rf_wthn_sev_rsq}$ for moderate and severe food insecurity, respectively), and excluding entire countries from the training data to evaluate out-of-country model error still showed overall good results ($R^2 = \myvar{rf_cv_mod_rsq}$ and $R^2 = \myvar{rf_cv_sev_rsq}$ for moderate and severe food insecurity, respectively).  The relative importance of different variables as predictors of food insecurity can be assessed by examining the loss in forecast accuracy resulting from the exclusion of particular covariates.

@@

\begin{figure}[h]
  \centering
  \includegraphics[width=\linewidth]{VIMP.pdf}
  \caption{Importance of each variable in predicting the percent of a population over thresholds for moderate and severe food insecurity.  This is determined by the increase in the error when the variable is permuted before fitting the model.}
  \label{fig:vimp}
\end{figure}

The results of this analysis can be further explored in more detail on the World Hunger Clock \href{https://worldhunger.io}{(worldhunger.io)}, including statistics for each subnational administrative area.

@@

It should be noted that our model was using covariates and making predictions a coarser scale - the administrative area - than much of the food security literature, which, since the 1990s, has increasing focused at the scale of the household \citep{Cooper2020}.  Thus, this analysis cannot speak to the localized impact of factors like climate, urbanization, or topography at the finer spatio-temporal scales at which these variables may operate \citep{Shukla2021, Blekking2020, Cockx2018, Tuholske2020}.  For example, our predictor variables for temperature and precipitation, derived from future simulations of the climate, can only model the effects of shifting baselines as data is smoothed over the course of the year - our model cannot anticipate the effects of short-term and extreme climate events on food insecurity.  Additionally, our model can only capture coarse, administrative area metrics of urbanization and cannot address household-level differences in food security between urban and rural households.  Nevertheless, the fact that these variables explained some of the variation in food security outcomes, even at administrative area scale, underscores their importance for food security.

Our results anticipating decreases in the number of people over the threshold for moderate food insecurity conflict with the FAO's predictions of increased rates of undernourishment, the other indicator for the SDG 2 target of ending hunger \citep[Part 1, Page 11]{sofi2020}.  However, severe food insecurity may be a more apt indicator to compare with undernourishment, as the global totals are more similar \citep{sofi2020}.  In this case, our predictions still diverge: the FAO estimates a 24\% increase, from 687 to 841 million undernourished people, from 2019 to 2030, whereas we predict a \myvar{decrprc_2019_2030_sev}\% decrease, from \myvar{sev_tot_2019} to \myvar{sev_tot_2030} million severely food insecure people over the same period.

@@

\printbibliography

>>>>

% Use datatool to read in reported values
% csv must have columns `var` and `val`
% \usepackage{datatool}
% \DTLsetseparator{,}
% \DTLloaddb{data}{vars.csv}
% \newcommand{\myvar}[1]{\DTLfetch{data}{var}{#1}{val}}

%\addbibresource{library.bib}

\bibliographystyle{splncs}

@@

Food security has traditionally been difficult to measure, and this has arguably led to an incomplete or possibly inaccurate assessment of global hunger. Metrics of macro-health, such as anthropometric measures and mortality rates are correlated broadly with food insecurity and have been used for many years to monitor human well-being \cite{Puffer1973, Habicht1974}.  However, these metrics are affected by other determinants of health such as the occurrence of infectious diseases, and are not meaningful at the scale of individuals or households \cite{Perumal2018}.  Other proxies for food security, such as food availability estimated from crop yields \cite{Maxwell1992}, are also inadequate because they only make rough estimates of how accessible food is to the general population, and can elide populations that are food insecure due to poor access, even when aggregate food availability is high \cite{Sen1983}.  Moreover, these metrics are very sensitive to incorrect estimates of crop yields and food reserves at a national scale.  Thus, global estimates of hunger and food insecurity based on these metrics carry forward similar flaws.

As researchers began to focus on food insecurity at the individual and household level, microdata from household surveys collecting information on household finances and consumption became a basis to compute a common proxy for food security \cite{Haddad1994}.  However, these efforts were criticized for being onerous, insufficiently comparable, as well as for ignoring subjective and experiential aspects of food security \cite{Maxwell1996}.  This led to the emergence of several indicators designed to be rapidly deployable, and based on the lived experience of food security \cite{Jones2013}.  These metrics include the Household Food Security Survey Module (HFSSM) \cite{kennedy2005keynote}, originally developed for use in the US; the Latin American and Caribbean Food Security Scale (ELCSA); and the Household Food Insecurity and Access Scale (HFIAS) \cite{Coates2007}.

Drawing on the insights derived in designing and implementing these novel food security metrics, the FIES was developed by the Food and Agricultural Organization (FAO) of the United Nations (UN) \cite{Ballard2013} and is now recognized as a rapidly deployable and cross-culturally valid tool for understanding individual and household-level food insecurity \cite{wambogo2018validity, smith2017world}.  The FIES is based on a survey of eight behaviors indicative of food insecurity and hunger over the previous year, such as skipping meals or worrying about having enough to eat.  Processing the responses given to the FIES questions through the Rasch model, each individual in the survey is assigned a score that allows them to be ranked on a scale of food insecurity severity. Once the severity measures are calibrated against a common reference (the global FIES reference scale) \cite{Cafiero2018} and individuals are ranked in this fashion, conventional thresholds for ``moderate'' and ``severe'' food insecurity are set and the prevalence of such food insecurity conditions can be computed. Thresholds are set in such a way that a moderately food insecure respondent is one who likely has compromised on food quality and variety as a result of lack of resources, has been unsure about their ability to obtain food and has skipped meals or run out of food occasionally. A severely food insecure one is likely to have run out of food and has gone an entire day without eating at times during the year.  The percentage of people estimated to be over the threshold set for moderate food insecurity includes people that are also over the threshold for severe food insecurity and represents the SDG indicator 2.1.2.

@@

\subsection{Disaggregation}
The data on the FIES collected by Gallup on behalf of FAO also records many individual-level attributes from the respondents, including age, gender, wealth quintile, and whether they live in an urban or rural area.  Using national data on these variables, a standard weighting scheme is created for each individual, based on the ratio of population probabilities to sample probabilities of an individual with those characteristics being selected \cite{bethlehem2009applied}.  This ensures that the results are representative at a national level.  We use a similar methodology, except that we calculate post-stratification weights at a subnational level.  We use year-specific subnational estimates of population shares by gender, age, urbanization, and, where available, wealth, and create a separate set of weights for each subnational area across all individuals.  For age and gender, we used gridded data from WorldPop \cite{Tatem2017}; for urbanization, we used spatially explicit estimates of population in urban and rural pixels published by Jones and O'Neill and deriving from night-time lights and buffered settlement centroids \cite{Jones2016}; and for wealth we used data on household wealth quintiles from Demographic and Health Surveys \cite{dhsall}.  This methodology rests on the mild assumption that, within a given country, two individuals of the same age, gender, urbanization level and wealth quintile will have a similar food security status, an assumption that underlies much of survey weighting methodology \cite{bethlehem2009applied}.

\subsection{Covariates}
We model subnational rates of moderate and severe food insecurity as a function of several covariates related to human development, nutrition, health, infrastructure, income levels and distribution, and the environment (See Table \ref{tab:covars}).  We employ covariates for which projections are available up to year 2030 and, in most cases, also have subnational spatial resolution.  For projections based on the Shared Socioeconomic Pathways (SSP) framework \cite{oneill2014new}, we use the middle-of-the-road pathway, SSP2, and for climatological variables, we use forecasts based on the Representative Concentration Pathway (RCP) 6.0 \cite{van2011representative}.

@@

For the climatic variables, mean annual temperature and total annual precipitation, we combine historical observations with an ensemble of four bias-corrected simulations of the future climate from the Inter-Sectoral Impact Model Intercomparison Project (ISIMIP) \cite{warszawski2014inter}.  These variables cannot speak to sudden shocks but do capture the climatic baselines relevant to agro-ecological conditions that constrain food production.

Finally, we adjust several variables to account for the effects of the COVID-19 pandemic.  These include June 2020 GDP predictions from the World Bank \cite{prospects2020}, August 2020 estimates of impacts on anthropometry from \textit{The Lancet} \cite{headey2020impacts}, as well as the Poverty Headcount Index \cite{Cuaresma2018}.

@@

\subsection{Modeling}
We fit two models for all subnational areas globally from 2010 to 2030: one for the percent of the population over the threshold for moderate food insecurity, and one for the percent of the population over the threshold for severe food insecurity.  We assessed several different modeling strategies and found that a random forest machine learning approach performed the best.  A comparison of random forest and LASSO (Least Absolute Shrinkage and Selection Operator) regressions are presented in the supplement, and additional approaches are presented in a graduate thesis by one of the authors \cite{muller2021}.   A random forest regression involves generating a large number of decision trees, each using different sub-samples of the data, and then aggregating the predictions of the decision trees.  This approach performs well in the presence of non-linearities and interaction effects among predictor variables \cite{hastie2009elements}.  By taking an ensemble of decision tree models, random forests introduce more variance and balance out the bias that is common to methods based on single decision trees \cite{friedman2001elements}. Given the bounded nature of our variables of interest, the random forest regression are applied to the logistically transformed rates.  We create our models using the \texttt{randomForestSRC} package in R \cite{ishwaran2019randomforestsrc}.

@@

When performing cross validation, it is typical to select observations at random.  However, in our training data we have multiple highly similar observations from each country across years and subnational areas, and we extend our model predictions to countries that were not found at all in our training data.  Thus, we perform a type of leave-one-out cross validation, where we leave out all of the data from one country for each iteration.  Thus, the model error after cross validation gives us a sense of how the model is performing in countries where FIES data was not collected.  By this validation metric, we find that our models perform well, with an $R^2$ of 0.787 and mean average error (MAE) of 0.07 for moderate food insecurity and an $R^2$ of 0.756 and a MAE of 0.037 for severe food insecurity.  After fitting models on the entire dataset, we observe a within-sample $R^2$ of 0.936 and an MAE of 0.038 for moderate food insecurity and an $R^2$ of 0.99 and a MAE of 0.007 for severe food insecurity.

After fitting the models, we examine the importance of the individual covariates in explaining rates of moderate and severe food insecurity. We use a common method of permutating each individual variable and re-running the regressions, and then determining the difference in MAE between the regression \cite{ishwaran2007variable, breiman2001random}.  This metric can provide some interpretability to model predictions.

@@

\section{Results}
\subsection{Food Insecurity over Time}
Globally, in the year 2020, we estimate that 820 million people are above the threshold for severe food insecurity, and 2.5 billion people are above the threshold for moderate food insecurity (See Fig. \ref{fig:timeseries}). These numbers are higher than the estimates in the 2020 FAO State of Food Insecurity (SOFI) report, which reports about 746 million severely food insecure people and 2 billion people experiencing at least moderate food insecurity in 2019 \cite{sofi2020}.

Under realistic scenario assumptions, we find recent increases in the number of moderate and severely food insecure people around the world, yet expect overall decreases from 2010 to 2030.  These changes are more slight for people who are at least moderately food insecure: in 2030, the number of moderately food insecure people will have decreased by 2.6\% since 2010, and the number of severely food insecure people will have decreased by 12.4\%.  While the number of moderately and severely food insecure people are modeled to decrease overall, they are projected to increase in lower income countries through 2030.

\begin{figure}[H]
  \centering
  % \includegraphics[width=\linewidth]{TimeSeries.pdf}
  \caption{Number of people over the thresholds for moderate and severe food insecurity, by World Bank income groups as of 2020.  Panel (A) shows the number of food insecure people with region totals stacked, to show global trends and totals over time.  Panel (B) shows regional totals compared against each other over time.}
  \label{fig:timeseries}
\end{figure}

@@

\begin{figure}[H]
  \centering
  % \includegraphics[width=\linewidth]{Rates.pdf}
  \caption{Percentage of the population over the threshold for moderate and severe food insecurity, by World Bank income groups as of 2020.}
  \label{fig:rates}
\end{figure}

@@

\begin{landscape}
\begin{figure}[h]
  \centering
  % \includegraphics[width=\linewidth]{FullMap.pdf}
  \caption{Spatial distribution of moderate and severe food insecurity for the years 2010, 2020, and 2030.}
  \label{fig:map}
\end{figure}
\end{landscape}

\subsection{Important Predictors of Food Insecurity}
Overall, our model was able to predict food insecurity with high accuracy in the countries for which training data was available ($R^2 = 0.936$ and $R^2 = 0.99$ for moderate and severe food insecurity, respectively), and excluding entire countries from the training data to evaluate out-of-country model error still showed overall good results ($R^2 = 0.787$ and $R^2 = 0.756$ for moderate and severe food insecurity, respectively).  The relative importance of different variables as predictors of food insecurity can be assessed by examining the loss in forecast accuracy resulting from the exclusion of particular covariates.

@@

\begin{figure}[H]
  \centering
  % \includegraphics[width=\linewidth]{VIMP.pdf}
  \caption{Importance of each variable in predicting the percent of a population over thresholds for moderate and severe food insecurity.  This is determined by the increase in the error when the variable is permuted before fitting the model.}
  \label{fig:vimp}
\end{figure}

The results of this analysis can be further explored in more detail on the World Hunger Clock (\href{https://worldhunger.io}{worldhunger.io}), including statistics for each subnational administrative area.

@@

It should be noted that our model was using covariates and making predictions a coarser scale - the administrative area - than much of the food security literature, which, since the 1990s, has increasing focused at the scale of the household \cite{Cooper2020}.  Thus, this analysis cannot speak to the localized impact of factors like climate, urbanization, or topography at the finer spatio-temporal scales at which these variables may operate \cite{Shukla2021, Blekking2020, Cockx2018, Tuholske2020}.  For example, our predictor variables for temperature and precipitation, derived from future simulations of the climate, can only model the effects of shifting baselines as data is smoothed over the course of the year - our model cannot anticipate the effects of short-term and extreme climate events on food insecurity.  Additionally, our model can only capture coarse, administrative area metrics of urbanization and cannot address household-level differences in food security between urban and rural households.  Nevertheless, the fact that these variables explained some of the variation in food security outcomes, even at administrative area scale, underscores their importance for food security.

Our results anticipating decreases in the number of people over the threshold for moderate food insecurity conflict with the FAO's predictions of increased rates of undernourishment, the other indicator for the SDG 2 target of ending hunger \cite[Part 1, Page 11]{sofi2020}.  However, severe food insecurity may be a more apt indicator to compare with undernourishment, as the global totals are more similar \cite{sofi2020}.  In this case, our predictions still diverge: the FAO estimates a 24\% increase, from 687 to 841 million undernourished people, from 2019 to 2030, whereas we predict a 9.4\% decrease, from 790 to 715 million severely food insecure people over the same period.

@@

%\printbibliography

\bibliography{library}
